---
title: "Embarassment Study Version 2 Analysis"
Author: [Juanshu Wu]
output:
  html_document:
    df_print: paged
---

#Load Data and calculating error rates on attention checks

```{r,warning = FALSE, message = FALSE}
library(tidyverse)
#Load Data
Dat <- read.csv("EmbarrassmentEnvyVersion2.csv", TRUE) 
Dat %>% filter(Gender == 1) %>% nrow()

#The percentage of people get wrong in Attention 1: correct answer coded value is 13.
nrow(Dat %>% filter( Attention.1!= 13 ))/nrow(Dat)


#The percentage of people get wrong in Attention 2( the math question) :correct answer coded value is 5.
nrow(Dat %>% filter( Attention2!= 5))/nrow(Dat)


#Percentage of people get wrong in both attention 1 and attention 2 :
nrow(Dat %>% filter( Attention2!= 5&Attention.1!= 13 ))/nrow(Dat)


#Percentage of people get wrong in attention 1 or attention 2 :
nrow(Dat %>% filter( Attention2!=5 |Attention.1!= 13 ))/nrow(Dat)

```
The percentage of people get wrong in Attention 1: $9.25\%$
The percentage of people get wrong in Attention 2: $2.5\%$
Percentage of people get wrong in both attention 1 and attention 2:$0.5\%$
Percentage of people get wrong in attention 1 or attention 2:$11.3\%$
#Is failing attention 2 a predictor of failing attention 1? 
```{r,warning = FALSE, message = FALSE}
#Create binary variable for attention 2 error  and attention 1 error 
Dat <- Dat %>% mutate(attention.1.error = if_else(Attention.1 == 13, "AC1 Correct" , "AC1 Incorrect"))
Dat <- Dat %>% mutate(attention.2.error = if_else(Attention2 == 5, "AC2 Correct" , "AC2 Incorrect"))
library(tidyverse)

# Visualize a graph to see the dependence of attention 2 and attention 1 
#ggplot(Dat %>% filter(!is.na(attention.1.error) & !is.na(attention.2.error)) ) +
  #aes(x = attention.1.error, fill = attention.2.error) +
  #geom_bar() +
  #scale_fill_hue() +
  #theme_minimal()+
  #labs(x = "Attention 1 Check" , y = " Subject Count")+
  #scale_fill_discrete(name = "Attention 2 Check")

#Chi-Square table
Dat1<- Dat %>% filter(!is.na(attention.1.error)&!is.na(attention.2.error))

table(Dat1$attention.1.error,Dat1$attention.2.error)

chisq.test(Dat$attention.1.error,Dat$attention.2.error)

``` 
The dependency of attention 1 check and attention 2 check is NOT significant 
X^2 tests: X^2 (**1**) = **0.39**, p=**0.5341**  
#Is Attention1/ Attention 2  a predictor of duration spent completing the study?       
```{r,warning = FALSE, message = FALSE}

#log transform the duration in seconds;

anova(lm(log(Duration..in.seconds.) ~ attention.1.error, data =  Dat))

anova(lm(log(Duration..in.seconds.) ~ attention.2.error, data =  Dat))


``` 
Attention 1 significantly predict log( Study Duration in secs): F(**1**,**386**) = **36.46**, p < **0.01**
Attention 2 does NOT significantly predict log( Study Duration in secs): F(**1**,**383**) = **1.45**, p = **0.23**

#Is sequential rating differences during dispositional envy scale a predictor of duration spent completing the study?    

```{r,warning = FALSE, message = FALSE}

#Calculate and mutate the column of sequential rating differences during dispositional envy scale:
Dat2<- Dat %>% filter(!is.na(Envy1)) %>% mutate(sequential_difference = abs(Envy1-Envy2)+abs(Envy2 -  Envy3)+abs(Envy3-Envy4)+abs(Envy4-Envy5)+abs(Envy5-Envy6)+abs(Envy6-Envy7)+abs(Envy7-Envy8))

#linear regression on sequential_difference predicting log transformed duration in seconds ;
anova(lm(log(Duration..in.seconds.) ~ sequential_difference, data =  Dat2))

#liner regression of attention 1 error predicting sequential difference. 
anova(lm(sequential_difference ~attention.1.error, data = Dat2))
``` 

Sequential difference significantly predicts log transformed duration in seconds:F(**1**,**386**) = **3.94**, p = **0.048** 
Sequential difference significantly predicts attention 1 error :F(**1**,**386**) = **9.51**, p < **0.01**
#Data wrangling
```{r,warning = FALSE, message = FALSE}
#Delete the participants' data that fail the attention checks
Dat_attention_check_passed <- Dat %>% filter(Attention.1 == 13 & Attention2 == 5)
type_gender_know <- Dat_attention_check_passed %>% select(Gender, ResponseId, starts_with(c("Body", "Judgment")))

#type_gender_know <- 
  #type_gender_know %>% 
 # rename(Body.Naked_1 = Body.Naked._1, Body.Naked_2 = Body.Naked._2)
test <- type_gender_know %>% 
  select(Gender, Body.Bowel_1, Body.Bowel_2)

test %>% pivot_longer(cols=c(Body.Bowel_1, Body.Bowel_2), names_to = "doctor_type", values_to = "scores", names_prefix="Body.Bowel_")

repeated_ready <- 
type_gender_know %>% 
  pivot_longer(cols = starts_with(c("Judgment", "Body")), 
                 values_to = "scores", 
                 names_to = (c("Type", "Sub", "Doctor")),
               names_pattern = c("(.*)\\.(.*)_(.)"))
```

#Plots

```{r,warning = FALSE, message = FALSE}
# Doctor and Type or Embarrassment on Rating

repeated_ready$Doctor <- as.factor(repeated_ready$Doctor)
repeated_ready$Doctor <- recode_factor(repeated_ready$Doctor, "1" = "NOT Know","2" = "Know")

repeated_ready%>% 
  ggplot() +
  aes(x = Doctor, color = Type, group = Type, y = scores) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")+
  labs(y = "Embarassment Rating")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
          ggtitle("Doctor and Type of Embarassment on Rating")+
          stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
           scale_y_continuous(limits = c(1, 7))
 
```

```{r,warning = FALSE, message = FALSE}
#Doctor and Gender on Embarassment Rating

repeated_ready$Gender <- as.factor(repeated_ready$Gender)
repeated_ready$Gender <- recode_factor(repeated_ready$Gender, "1" = "Male","2" = "Female")

 repeated_ready %>% ggplot() +
  aes(x = Doctor, color = Gender, group = Gender, y = scores) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")+
  labs(y = "Embarassment Rating")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
   stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
  ggtitle("Doctor and Gender on Embarassment Rating")+
    scale_y_continuous(limits = c(1, 7))
 
 


```

```{r,warning = FALSE, message = FALSE}
#Embarassment Type and Gender on Embarassment Rating

 repeated_ready %>% ggplot() +
   aes(x = Type, color = Gender, group = Gender, y = scores) +
   stat_summary(fun.y = mean, geom = "point") +
   stat_summary(fun.y = mean, geom = "line")+
   labs(y = "Embarassment Rating")+
   theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"))+ 
   stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
   ggtitle("Type of embarassment and Gender on Rating")+
   scale_y_continuous(limits = c(1, 7))
 
 
 

```


```{r,warning = FALSE, message = FALSE}
# Doctor and SubTypes of Embarassment on Rating

repeated_ready%>% 
  ggplot() +
  aes(x = Doctor, color = Sub, group = Sub, y = scores) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")+
  labs(y = "Embarassment Rating")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
  ggtitle("Doctor and SubTypes of Embarassment on Rating")+
  stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
   facet_wrap(.~Type)+
   scale_y_continuous(limits = c(1, 7))
 
```
 
 
```{r,warning = FALSE, message = FALSE}

 repeated_ready%>% 
  ggplot() +
  aes(x = Doctor, color = Type, group = Type, y = scores) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")+
  labs(y = "Embarassment Rating")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
          ggtitle("Doctor/Gender/Type of Embarassment on Rating")+
          stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
          facet_wrap(.~ Gender)+scale_y_continuous(limits = c(1, 7))
 
 
``` 
 
#Repeated Measure Full Model
 
```{r,warning = FALSE, message = FALSE}
model1<- aov(scores ~ Gender*Type*Doctor+Error(ResponseId/(Type*Doctor)), data = repeated_ready)
summary(model1)
plot(fitted(model1),residuals(model1))

```
Significant interaction of Doctor type and Embarrassment type: F(**1**,**339**) = **36.03**, p <**0.01**
 
Significant interaction of Gender and Embarrassment type: F(**1**,**339**) = **4.78**, p = **0.03**
 
Non-Significant interaction of Gender and Doctor type: F(**1**,**339**) = **0.006**, p = **0.94**

Non-Significant  three-way interaction of Gender/Doctor type/Embarrassment type: F(**1**,**339**) = **3.15**, p = **0.077**
 
Significant Main effect of Gender: F(**1**,**339**) = **16.22**, p < **0.01**
 
Significant Main effect of Doctor type: F(**1**,**339**) = **7.7**, p < **0.01**
 
Significant Main effect of Embarrassment type: F(**1**,**339**) = **7.15**, p = **0.011**
 


















