---
title: "Envy Data Collection12 Combined"
author: "Juanshu Wu"
date: "3/22/2021"
output: html_document
---
#Load data and combine two collected datasets to one envy dataset/Create Envy variables.

```{r,warning = FALSE, message = FALSE}

library(tidyverse)

#Load data collection 1 

data1 <-  read.csv("EmbarrassmentEnvyVersion1.csv", TRUE)%>% filter(Attention.1 == 13 & Attention2 == 5) %>%select(General.Enjoy.Envied,     
Personal.Achievement,   
Physical.Attractive,      
Academic.Achievement,     
Popularity, Envy1,Envy2,Envy3,Envy4,Envy5,Envy6,Envy7,Envy8,
B1,B2,B3,B4,
M1,M2,M3,M4)

#Load data collection 2
data2 <- read.csv("EmbarrassmentEnvyVersion2.csv",TRUE)%>%
filter(Attention.1 == 13 & Attention2 == 5)%>%
select(General.Enjoy.Envied,     
Personal.Achievement,   
Physical.Attractive,      
Academic.Achievement,     
Popularity, Envy1,Envy2,Envy3,Envy4,Envy5,Envy6,Envy7,Envy8,
B1,B2,B3,B4,
M1,M2,M3,M4) 

#Combine data 1 and data 2
Envy_combined<- rbind(data1,data2)

#Filter out NAs
Envy_combined_cleaned<- Envy_combined %>% filter (!is.na(General.Enjoy.Envied))%>%filter (!is.na(Envy1))

#Create variable dispositional envy as the average of all the eight  dispositional envy items
Envy_combined_cleaned <- Envy_combined_cleaned %>% mutate(Disp_envy = (Envy1+Envy2+Envy3+Envy4+Envy5+Envy6+Envy7+Envy8)/8)

#Create variable Benvy as the average of all the benign envy items
Envy_combined_cleaned<- Envy_combined_cleaned %>% mutate(Benvy = ((B1+B2+B3+B4)/4))

#Create variable Menvy as the average of all the malicious envy items
Envy_combined_cleaned <- Envy_combined_cleaned %>% mutate(Menvy = ((M1+M2+M3+M4)/4))

#Create variable Scenarios.Enjoy.Envied as the average of the all the scenarios of enjoyment of being envied

Envy_combined_cleaned <- Envy_combined_cleaned %>% mutate(Scenarios.Enjoy.Envied = (Personal.Achievement+Physical.Attractive+Academic.Achievement+Popularity)/4)


```

#Check and Plot  Correlation of Disp_envy(dispositional envy )and General.Enjoy.Envied("How in general do you like being envied the this person( in recalled envy event))

```{r,warning = FALSE, message = FALSE}
#Correlation Test
cor.test(Envy_combined_cleaned$Disp_envy,Envy_combined_cleaned$General.Enjoy.Envied)


#Plot 

ggplot(Envy_combined_cleaned, aes(x= Disp_envy, y = General.Enjoy.Envied))+
  geom_jitter()+
  labs(y = "General.Enjoy.Envied", x = "mean Dispositional Envy")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
         geom_smooth(method = lm)+
         ggtitle("Recall Enjoyment of Envy / Dispositional Envy")

```


**Report:** Dispositional envy significantly correlated with General enjoyment of envy in the past recalled event of being envied: r(**354**) = **0.27**, p < **0.01**





#Check and Plot  Correlation of Disp_envy(dispositional envy )and Scenarios.Enjoy.Envied( average enjoyment of envy across four scenarios(e.g. popularity))

```{r,warning = FALSE, message = FALSE}
#Correlation Test
cor.test(Envy_combined_cleaned$Disp_envy,Envy_combined_cleaned$Scenarios.Enjoy.Envied)


#Plot 
ggplot(Envy_combined_cleaned, aes(x= Disp_envy, y = Scenarios.Enjoy.Envied))+
  geom_jitter()+
  labs(y = "Scenarios.Enjoy.Envied", x = "mean Dispositional Envy")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
         geom_smooth(method = lm)+
         ggtitle("Scenarios.Enjoy.Envied / Dispositional Envy")

```


**Report:** Dispositional envy significantly correlated with average enjoyment  of envy across the four hypothetical being envied scenarios: r(**353**) = **0.32**, p < **0.01**


#Check and Plot  Correlation of Benvy (average benign envy) and Scenarios.Enjoy.Envied( average enjoyment of envy across four scenarios(e.g. popularity))

```{r,warning = FALSE, message = FALSE}
#Correlation Test
cor.test(Envy_combined_cleaned$Benvy,Envy_combined_cleaned$Scenarios.Enjoy.Envied)
#Plot 
ggplot(Envy_combined_cleaned, aes(x= Benvy, y = Scenarios.Enjoy.Envied))+
  geom_jitter()+
  labs(y = "Scenarios.Enjoy.Envied", x = "mean Benign Envy")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
         geom_smooth(method = lm)+
         ggtitle("Scenarios.Enjoy.Envied / Benign Envy")

```


**Report:** Benign envy significantly correlated with average enjoyment  of envy across the four hypothetical being envied scenarios: r(**353**) = **0.34**, p < **0.01**



#Check and Plot  Correlation of Benvy (average benign envy) and General.Enjoy.Envied("How in general do you like being envied the this person( in recalled envy event))


```{r,warning = FALSE, message = FALSE}
#Correlation Test
cor.test(Envy_combined_cleaned$Benvy,Envy_combined_cleaned$General.Enjoy.Envied)

#Plot 

ggplot(Envy_combined_cleaned, aes(x= Benvy, y = General.Enjoy.Envied))+
  geom_jitter()+
  labs(y = "General.Enjoy.Envied", x = "mean Benign Envy")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
         geom_smooth(method = lm)+
         ggtitle("Recall Enjoyment of Envy / Benign Envy")

```

**Report:** Benign envy significantly correlated with  General enjoyment of envy in the past recalled event of being envied: r(**354**) = **0.26**, p < **0.01**



#Check and Plot  Correlation of Menvy (average malicious envy) and Scenarios.Enjoy.Envied( average enjoyment of envy across four scenarios(e.g. popularity))

```{r,warning = FALSE, message = FALSE}
#Correlation Test
cor.test(Envy_combined_cleaned$Menvy,Envy_combined_cleaned$Scenarios.Enjoy.Envied)


#Plot 
ggplot(Envy_combined_cleaned, aes(x= Menvy, y = Scenarios.Enjoy.Envied))+
  geom_jitter()+
  labs(y = "Scenarios.Enjoy.Envied", x = "mean Malicious Envy")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
         geom_smooth(method = lm)+
         ggtitle("Scenarios.Enjoy.Envied / Malicious Envy")

```

**Report:** Malicious  envy significantly correlated with average enjoyment  of envy across the four hypothetical being envied scenarios: r(**353**) = **0.39**, p < **0.01**



#Check and Plot  Correlation of Menvy (average malicious envy) and General.Enjoy.Envied("How in general do you like being envied the this person( in recalled envy event))


```{r,warning = FALSE, message = FALSE}
#Correlation Test
cor.test(Envy_combined_cleaned$Menvy,Envy_combined_cleaned$General.Enjoy.Envied)

#Plot 

ggplot(Envy_combined_cleaned, aes(x= Benvy, y = General.Enjoy.Envied))+
  geom_jitter()+
  labs(y = "General.Enjoy.Envied", x = "mean Malicious Envy")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
         geom_smooth(method = lm)+
        ggtitle("Recall Enjoyment of Envy / Malicious Envy")

```


**Report:** Malicious envy significantly correlated with  General enjoyment of envy in the past recalled event of being envied: r(**354**) = **0.31**, p < **0.01**


```{r,warning = FALSE, message = FALSE}
install.packages("lme4")
library(lme4)

#Section ----Type; part-----Sub; test----Doctor:Sex-Gender:  student---Prolific ID
m <- lmer(data= repeated_ready1, scores~Gender*Doctor*Type
+(1|Prolific.ID)+(1|Prolific.ID:Doctor)+(1|Prolific.ID:Type)+(1|Prolific.ID:Doctor:Type)
+(1|Sub+(1|Sub:Doctor)+(1|Sub:Gender)+(1|Sub:Doctor:Gender)
+(1|Prolific.ID:part))


summary(m)


```





