---
title: "Free Speech"
author: "Juanshu Wu"
date: "7/9/2021"
output:
  html_document: default
  pdf_document: default
---
#Load data and delete data who failed to consent or failed the attention check
```{r,warning = FALSE, message = FALSE}
#Load data
library(tidyverse)
Dat <- read.csv("FreeSpeech.csv",TRUE)
#Only keep participants who consent to participate
Dat1 <- Dat %>% filter(Consent == "1") 
#Delete the participants' data that fail the attention checks
Dat_attention_check_passed <- Dat1 %>% filter(Attention1 == 1)
```

#Categorize people into left and right slant

```{r,warning = FALSE, message = FALSE}
Dat_filtered <- Dat_attention_check_passed %>% filter( Ideology != 9 | PoliticalParty!= 9)
Dat_filtered <- Dat_filtered %>% mutate(politicalslant = Ideology+PoliticalParty)
Dat_filtered <- Dat_filtered %>% filter(politicalslant != 0)
Dat_filtered$Political_Slant<-ifelse(Dat_filtered$politicalslant > 0,"right","left")
```

#Recode values
```{r,warning = FALSE, message = FALSE}

Dat_filtered$X1.Prohibited = recode_factor(Dat_filtered$X1.Prohibited,"1"= "Yes","2" = "No","3" = "Not Sure")
Dat_filtered$X1.StudentAllow = recode_factor(Dat_filtered$X1.StudentAllow,"1"= "Yes","2" = "No","3" = "Not Sure")
Dat_filtered$X1.FacultyAllow = recode_factor(Dat_filtered$X1.FacultyAllow,"1"= "Yes","2" = "No","3" = "Not Sure")
Dat_filtered$X1.LibraryAllow= recode_factor(Dat_filtered$X1.LibraryAllow,"1"= "Yes","2" = "No","3" = "Not Sure")
Dat_filtered$X2.Prohibited = recode_factor(Dat_filtered$X2.Prohibited,"1"= "Yes","2" = "No","3" = "Not Sure")
Dat_filtered$X2.StudentAllow = recode_factor(Dat_filtered$X2.StudentAllow,"1"= "Yes","2" = "No","3" = "Not Sure")
Dat_filtered$X2.FacultyAllow = recode_factor(Dat_filtered$X2.FacultyAllow,"1"= "Yes","2" = "No","3" = "Not Sure")
Dat_filtered$X2.LibraryAllow= recode_factor(Dat_filtered$X2.LibraryAllow,"1"= "Yes","2" = "No","3" = "Not Sure") 

```

#StudentAllow Proportion for most harmful belief(Political Slant) 
```{r,warning = FALSE, message = FALSE}
#Chi_Square
chisq.test(Dat_filtered$Political_Slant,Dat_filtered$X1.StudentAllow)

#Stacked
ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  geom_bar(position="fill")+theme (plot.title = element_text(hjust = 0.5),text = element_text(family = "serif", size = 12),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle(" (1) a student allowed by their university to publicly express this belief ")+labs(y = "Proportion", x = "Political Slant",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#Prohibited proportion for most harmful belief(Political Slant)
```{r,warning = FALSE, message = FALSE}
#Chi_Square
chisq.test(Dat_filtered$Political_Slant,Dat_filtered$X1.Prohibited)
  
# stacked
ggplot(Dat_filtered, aes(Political_Slant, fill=X1.Prohibited)) + 
  geom_bar(position="fill")+theme(plot.title = element_text(hjust = 0.5),text = element_text(family = "serif",size = 12),panel.grid.major = element_blank(), panel.grid.minor =element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(1)Prohibited in US for people to express this belief publicly?")+labs(y = "Proportion", x = "Political Slant",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#FacultyAllow proportion for most harmful belief(Political Slant)
```{r,warning = FALSE, message = FALSE}
chisq.test(Dat_filtered$Political_Slant,Dat_filtered$X1.FacultyAllow)
  
# stacked
ggplot(Dat_filtered, aes(Political_Slant, fill=X1.FacultyAllow)) + 
  geom_bar(position="fill")+theme(plot.title = element_text(hjust = 0.5),text = element_text(family = "serif",size = 12),panel.grid.major = element_blank(), panel.grid.minor =element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(1)Allow faculty member in University to express this belief publicly?")+labs(y = "Proportion", x = "Political Slant",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#Library allow porpotion for most harmful belief(Political Slant)
```{r,warning = FALSE, message = FALSE}
chisq.test(Dat_filtered$Political_Slant,Dat_filtered$X1.LibraryAllow)
  
# stacked
ggplot(Dat_filtered, aes(Political_Slant, fill=X1.LibraryAllow)) + 
  geom_bar(position="fill")+theme(plot.title = element_text(hjust = 0.5),text = element_text(family = "serif",size = 12),panel.grid.major = element_blank(), panel.grid.minor =element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(1)library should ban this belief?")+labs(y = "Proportion", x = "Political Slant",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```


#Student Allow proportion for second most harmful belief(Political Slant)
```{r,warning = FALSE, message = FALSE}
chisq.test(Dat_filtered$Political_Slant,Dat_filtered$X2.StudentAllow)
  
# stacked
ggplot(Dat_filtered, aes(Political_Slant, fill=X2.StudentAllow)) + 
  geom_bar(position="fill")+theme (plot.title = element_text(hjust = 0.5),text = element_text(family = "serif", size = 12),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+ggtitle("(2) a student allowed by their university to publicly express this belief")+labs(y ="Proportion", x = "Political Slant",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#Prohibited proprotion for second most harmful belief(Political Slant)
```{r,warning = FALSE, message = FALSE}
chisq.test(Dat_filtered$Political_Slant,Dat_filtered$X2.Prohibited)
  
# stacked
ggplot(Dat_filtered, aes(Political_Slant, fill=X2.Prohibited)) + 
  geom_bar(position="fill")+theme(plot.title = element_text(hjust = 0.5),text = element_text(family = "serif",size = 12),panel.grid.major = element_blank(), panel.grid.minor =element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(2)Prohibited in US for people to express this belief publicly?")+labs(y = "Proportion", x = "Political Slant",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#FacultyAllow proportion for second most harmful belief(Political Slant)
```{r,warning = FALSE, message = FALSE}

chisq.test(Dat_filtered$Political_Slant,Dat_filtered$X2.FacultyAllow)
# stacked
ggplot(Dat_filtered, aes(Political_Slant, fill=X2.FacultyAllow)) + 
  geom_bar(position="fill")+
  theme(plot.title = element_text(hjust = 0.5),text = element_text(family = "serif",size = 12),panel.grid.major = element_blank(), panel.grid.minor =element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(2)Allow faculty member in University to express this belief publicly?")+labs(y = "Proportion", x = "Political Slant",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#LibraryAllow proportion for second most harmful belief(Political Slant)
```{r,warning = FALSE, message = FALSE}

chisq.test(Dat_filtered$Political_Slant,Dat_filtered$X2.LibraryAllow)
# stacked
ggplot(Dat_filtered, aes(Political_Slant, fill=X2.LibraryAllow)) + 
  geom_bar(position="fill")+theme(plot.title = element_text(hjust = 0.5),text = element_text(family = "serif",size = 12),panel.grid.major = element_blank(), panel.grid.minor =element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(2)library should ban this belief?")+labs(y = "Proportion", x = "Political Slant",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#recode Gender
```{r,warning = FALSE, message = FALSE}
#Recode Gender numeric value into gender category
Dat_filtered$Gender= recode_factor(Dat_filtered$Gender,"1"= "Male","2" = "Female")

```

#StudentAllow Proportion for most harmful belief(Gender) 
```{r,warning = FALSE, message = FALSE}
#Chi_Square
chisq.test(Dat_filtered$Gender,Dat_filtered$X1.StudentAllow)

#Stacked
ggplot(Dat_filtered, aes(Gender, fill=X1.StudentAllow)) + 
  geom_bar(position="fill")+theme (plot.title = element_text(hjust = 0.5),text = element_text(family = "serif", size = 12),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(1) a student allowed by their university to publicly express this belief(Gender)")+labs(y = "Proportion", x = "Gender",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#Prohibited proportion for most harmful belief(Gender)
```{r,warning = FALSE, message = FALSE}
#Chi_Square
chisq.test(Dat_filtered$Gender,Dat_filtered$X1.Prohibited)
  
# stacked
ggplot(Dat_filtered, aes(Gender, fill=X1.Prohibited)) + 
  geom_bar(position="fill")+theme(plot.title = element_text(hjust = 0.5),text = element_text(family = "serif",size = 12),panel.grid.major = element_blank(), panel.grid.minor =element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(1) prohibited in US for people to express this belief publicly?")+labs(y = "Proportion", x = "Gender",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#FacultyAllow proportion for most harmful belief(Gender)
```{r,warning = FALSE, message = FALSE}
chisq.test(Dat_filtered$Gender,Dat_filtered$X1.FacultyAllow)
  
# stacked
ggplot(Dat_filtered, aes(Gender, fill=X1.FacultyAllow)) + 
  geom_bar(position="fill")+theme(plot.title = element_text(hjust = 0.5),text = element_text(family = "serif",size = 12),panel.grid.major = element_blank(), panel.grid.minor =element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(1)Allow faculty member in University to express this belief publicly?")+labs(y = "Proportion", x = "Gender",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#Library allow porpotion for most harmful belief(Gender)
```{r,warning = FALSE, message = FALSE}
chisq.test(Dat_filtered$Gender,Dat_filtered$X1.LibraryAllow)
  
# stacked
ggplot(Dat_filtered, aes(Gender, fill=X1.LibraryAllow)) + 
  geom_bar(position="fill")+theme(plot.title = element_text(hjust = 0.5),text = element_text(family = "serif",size = 12),panel.grid.major = element_blank(), panel.grid.minor =element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(1)library should ban this belief?")+labs(y = "Proportion", x = "Gender",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```


#Student Allow proportion for second most harmful belief(Gender)
```{r,warning = FALSE, message = FALSE}
chisq.test(Dat_filtered$Gender,Dat_filtered$X2.StudentAllow)
  
# stacked
ggplot(Dat_filtered, aes(Gender, fill=X2.StudentAllow)) + 
  geom_bar(position="fill")+theme (plot.title = element_text(hjust = 0.5),text = element_text(family = "serif", size = 12),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+ggtitle("(2) a student allowed by their university to publicly express this belief")+labs(y ="Proportion", x = "Gender",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#Prohibited proprotion for second most harmful belief(Gender)
```{r,warning = FALSE, message = FALSE}
chisq.test(Dat_filtered$Gender,Dat_filtered$X2.Prohibited)
  
# stacked
ggplot(Dat_filtered, aes(Gender, fill=X2.Prohibited)) + 
  geom_bar(position="fill")+theme(plot.title = element_text(hjust = 0.5),text = element_text(family = "serif",size = 12),panel.grid.major = element_blank(), panel.grid.minor =element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(2)Prohibited in US for people to express this belief publicly?")+labs(y = "Proportion", x = "Gender",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#FacultyAllow proportion for second most harmful belief(Gender)
```{r,warning = FALSE, message = FALSE}

chisq.test(Dat_filtered$Gender,Dat_filtered$X2.FacultyAllow)
# stacked
ggplot(Dat_filtered, aes(Gender, fill=X2.FacultyAllow)) + 
  geom_bar(position="fill")+
  theme(plot.title = element_text(hjust = 0.5),text = element_text(family = "serif",size = 12),panel.grid.major = element_blank(), panel.grid.minor =element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(2)Allow faculty member in University to express this belief publicly?")+labs(y = "Proportion", x = "Political Slant",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```

#LibraryAllow proportion for second most harmful belief(Gender)
```{r,warning = FALSE, message = FALSE}

chisq.test(Dat_filtered$Gender,Dat_filtered$X2.LibraryAllow)
# stacked
ggplot(Dat_filtered, aes(Gender, fill=X2.LibraryAllow)) + 
  geom_bar(position="fill")+theme(plot.title = element_text(hjust = 0.5),text = element_text(family = "serif",size = 12),panel.grid.major = element_blank(), panel.grid.minor =element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("(2)library should ban this belief?")+labs(y = "Proportion", x = "Gender",fill = "Answer choice")

# bar dodged
#ggplot(Dat_filtered, aes(Political_Slant, fill=X1.StudentAllow)) + 
  #geom_bar(position="dodge")

```















