---
title: "Prolific Embarassment Envy Chaperone Study"
author: "Juanshu Wu"
date: "5/16/2021"
output: html_document
---
#Data wrangling
```{r,warning = FALSE, message = FALSE}
#Load data
library(tidyverse)
Dat <- read.csv("Prolific-500participants-Numeric.csv",TRUE)
Dat1 <- Dat %>% filter(Consent == "1") 
nrow(Dat1 %>% filter( HighestDegree == 8))

STRANGE <- Dat1 %>% filter(is.na(Attention1))

#Delete the participants' data that fail the attention checks
Dat_attention_check_passed <- Dat1 %>% filter(Attention1 == 1)
Dat_attention_check_failed <- Dat1 %>% filter(Attention1 != 1)


type_gender_know <- Dat_attention_check_passed %>% select(Gender, Prolific.ID, starts_with(c("Body","Judgment")))
#type_gender_know <- 
  #type_gender_know %>% 
 # rename(Body.Naked_1 = Body.Naked._1, Body.Naked_2 = Body.Naked._2)
test <- type_gender_know %>% select(Gender, Body.Bowel_1, Body.Bowel_2)

test %>% pivot_longer(cols=c(Body.Bowel_1, Body.Bowel_2), names_to = "doctor_type", values_to = "scores", names_prefix="Body.Bowel_")

repeated_ready1 <- 
type_gender_know %>% 
  pivot_longer(cols = starts_with(c("Judgment", "Body")), 
                 values_to = "scores", 
                 names_to = (c("Type", "Sub", "Doctor")),
               names_pattern = c("(.*)\\.(.*)_(.)"))
```


```{r,warning = FALSE, message = FALSE}
# Doctor and Type or Embarrassment on Rating

repeated_ready1$Doctor <- as.factor(repeated_ready1$Doctor)
repeated_ready1$Doctor <- recode_factor(repeated_ready1$Doctor, "1" = "NOT Know","2" = "Know")

repeated_ready1%>% 
  ggplot() +
  aes(x = Doctor, color = Type, group = Type, y = scores) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")+
  labs(y = "Embarassment Rating")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
          ggtitle("Doctor and Type of Embarassment on Rating")+
          stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
           scale_y_continuous(limits = c(1, 7))
 
```



```{r,warning = FALSE, message = FALSE}
# Gender and Type of Embarrassment on Rating
repeated_ready1$Gender <- as.factor(repeated_ready1$Gender)
repeated_ready1$Gender<- recode_factor(repeated_ready1$Gender, "1" = "Male","2" = "Female")
repeated_ready1%>% 
  ggplot() +
  aes(x = Type, color = Gender, group = Gender, y = scores) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")+
  labs(y = "Embarassment Rating")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
          ggtitle("Gender and Type of Embarassment on Rating")+
          stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
           scale_y_continuous(limits = c(1, 7))
 
```

```{r,warning = FALSE, message = FALSE}
# Doctor and SubTypes of Embarassment on Rating
repeated_ready1%>% 
  ggplot() +
  aes(x = Doctor, color = Sub, group = Sub, y = scores) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")+
  labs(y = "Embarassment Rating")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
  ggtitle("Doctor and SubTypes of Embarassment on Rating")+
  stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
   facet_wrap(.~Type)+
   scale_y_continuous(limits = c(1, 7))

 
```



```{r,warning = FALSE, message = FALSE}
## A sequential ANOVA approach


library(lme4)
m1 <- lmer(data=repeated_ready1, scores~1
+(1|Prolific.ID)+(1|Prolific.ID:Type)+(1|Prolific.ID:Doctor)+(1|Prolific.ID:Type:Doctor))
m2 <- lmer(data=repeated_ready1,scores~Gender+(1|Prolific.ID)+(1|Prolific.ID:Type)+(1|Prolific.ID:Doctor)+(1|Prolific.ID:Type:Doctor))
anova(m1,m2)
m3 <- lmer(data=repeated_ready1, scores~Gender+Type
+(1|Prolific.ID)+(1|Prolific.ID:Type)+(1|Prolific.ID:Doctor)+(1|Prolific.ID:Type:Doctor))
anova(m1,m2)
m4<- lmer(data=repeated_ready1, scores~Gender+Type+Doctor
+(1|Prolific.ID)+(1|Prolific.ID:Type)+(1|Prolific.ID:Doctor)+(1|Prolific.ID:Type:Doctor))
anova(m1,m2)
m5<- lmer(data=repeated_ready1,scores~Gender+Type+Doctor+Gender:Type+(1|Prolific.ID)+(1|Prolific.ID:Type)+(1|Prolific.ID:Doctor)+(1|Prolific.ID:Type:Doctor))
m6<- lmer(data=repeated_ready1,scores~Gender+Type+Doctor+Gender:Type+ Type:Doctor+(1|Prolific.ID)+(1|Prolific.ID:Type)+(1|Prolific.ID:Doctor)+(1|Prolific.ID:Type:Doctor))
m7 <- lmer(data=repeated_ready1,scores~Gender+Type+Doctor+Gender:Type+ Type:Doctor+ Gender:Doctor+(1|Prolific.ID)+(1|Prolific.ID:Type)+(1|Prolific.ID:Doctor)+(1|Prolific.ID:Type:Doctor))
m8 <- lmer(data=repeated_ready1,scores~Gender+Type+Doctor+Gender:Type+ Type:Doctor+ Gender:Doctor+ Type:Doctor:Gender+(1|Prolific.ID)+(1|Prolific.ID:Type)+(1|Prolific.ID:Doctor)+(1|Prolific.ID:Type:Doctor))

##Compare model:
anova(m1,m2)
anova(m2,m3)
anova(m3,m4)
anova(m4,m5)
anova(m5,m6)
anova(m6,m7)
anova(m7,m8)



```

**Only significant result reported here**
Significant main effect of Gender: Adding the explanatory variable Gender significantly improves the model: Chisq(1) = $24.57$, p < $0.001$
Significant interaction of Doctor type and Embarrassment type: Adding the explanatory variable "Doctor: Type "significantly improves the model: Chisq(1)= $127.8$, p < $0.001$
Significant interaction of Gender and Embarrassment type: Adding the explanatory variable "Doctor: Type "significantly improves the model: Chisq(1)=  $4.87$ , p = $0.02$

```{r,warning = FALSE, message = FALSE}

Dat1<- Dat_attention_check_passed %>% mutate(DispEnvy = (Envy1+Envy2+Envy3+Envy4+Envy5+Envy6+Envy7+Envy8)/8)
Dat1<- Dat1 %>% mutate(EnviedPreference=(Envied.PA.Preference+Envied.FC.Preference)/2)
Dat1<- Dat1 %>% mutate(EnviedEnjoyment=(Envied.PA.Enjoyment+Envied.FC.Enjoyment)/2)
```

```{r,warning = FALSE, message = FALSE}
ggplot(Dat1, aes(x= DispEnvy, y = Dat1$Envied.Enjoyment))+
  geom_jitter()+
  labs(y = "Envied-Enjoyment-Recall", x = "mean Dispositional Envy")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+ geom_smooth(method = lm)+ ggtitle("Recall Enjoyment of Envy / Dispositional Envy")

cor.test(Dat1$DispEnvy,Dat1$Envied.Enjoyment)


```

**Report:** Dispositional envy significantly correlated with enjoyment of being envied in the past recalled event of being envied: r(**285**) = **0.133**, p = **0.024**


```{r,warning = FALSE, message = FALSE}

ggplot(Dat1, aes(x= DispEnvy, y = Dat1$EnviedPreference))+
  geom_jitter()+
  labs(y = "Envied-Preference", x = "mean Dispositional Envy")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
         geom_smooth(method = lm)+
         ggtitle("Being Envied Preference / Dispositional Envy")

cor.test(Dat1$DispEnvy,Dat1$EnviedPreference)


```
**Report:** Dispositional envy significantly correlated with preference for being  envied-inducing situations : r(**493**) = **0.133**, p = **0.003**


```{r,warning = FALSE, message = FALSE}

ggplot(Dat1, aes(x= DispEnvy, y = Dat1$EnviedEnjoyment))+
  geom_jitter()+
  labs(y = "Envied-Enjoyment", x = "mean Dispositional Envy")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
         geom_smooth(method = lm)+
         ggtitle("Envied-Enjoyment / Dispositional Envy")


cor.test(Dat1$DispEnvy,Dat1$EnviedEnjoyment)

```
**Report:** Dispositional envy significantly correlated with preference for being  envied-inducing situations : r(**493**) = **0.23**, p < **0.001**






```{r,warning = FALSE, message = FALSE}
# A sequential ANOVA approach
library(tidyverse)
repeated_ready_avg <- repeated_ready1 %>% group_by(Doctor,Type,Prolific.ID,Gender)%>% summarize(score_avg = mean(scores))

install.packages("lme4")
library(lme4)

m1 <- lmer(data=repeated_ready_avg, score_avg~1+(1|Prolific.ID))
m2 <- lmer(data=repeated_ready_avg,score_avg~Gender+(1|Prolific.ID))
anova(m1,m2)
m3 <- lmer(data=repeated_ready_avg, score_avg~Gender+Type
+(1|Prolific.ID))
anova(m1,m2)
m4<- lmer(data=repeated_ready_avg, score_avg~Gender+Type+Doctor
+(1|Prolific.ID))
anova(m1,m2)
m5<- lmer(data=repeated_ready_avg,score_avg~Gender+Type+Doctor+Gender:Type+(1|Prolific.ID))
m6<- lmer(data=repeated_ready_avg,score_avg~Gender+Type+Doctor+Gender:Type+ Type:Doctor+(1|Prolific.ID))
          
m7 <- lmer(data=repeated_ready_avg,score_avg~Gender+Type+Doctor+Gender:Type+ Type:Doctor+ Gender:Doctor+(1|Prolific.ID))
           
m8 <- lmer(data=repeated_ready_avg,score_avg~Gender+Type+Doctor+Gender:Type+ Type:Doctor+ Gender:Doctor+ Type:Doctor:Gender+(1|Prolific.ID))


library(lmerTest)
summary(m8)

           
          
##Compare model:
anova(m1,m2)
anova(m2,m3)
anova(m3,m4)
anova(m4,m5)
anova(m5,m6)
anova(m6,m7)
anova(m7,m8)
```






















1.	was this physician you'd seen before-> did you misrepresent...?
```{r,warning = FALSE, message = FALSE}

DataA1 <- Dat_attention_check_passed %>% filter(Mispresent != 3 & Physician.Previous != 3)
DataA1$Mispresent = recode_factor(DataA1$Mispresent, "1" = "Misrepresent-Yes","2" = "Misrepresent-NO")
DataA1$Physician.Previous = recode_factor(DataA1$Physician.Previous, "1" = "PreviousSeenPhysician-Yes","2" = "PreviousSeenPhysician-No")

table(DataA1$Physician.Previous,DataA1$Mispresent)

chisq.test(DataA1$Physician.Previous,DataA1$Mispresent)

anova(A1, test = 'LRT')

```
**Whether the physician is someone the participant had seen before does not significantly predict people misrepresent unfavorable information: Chisq(1) = 0.81957,p-value = 0.3653**

2.Gender-PT (patient) X gender-doc -> how much embar or awkwardness...?

```{r,warning = FALSE, message = FALSE}
DataA2 <- Dat_attention_check_passed %>% filter(Physician.Gender != 3)
DataA2$Gender = recode_factor(DataA2$Gender, "1"= "Male","2" = "Female")
DataA2$Physician.Gender= recode_factor(DataA2$Physician.Gender, "1" = "Male", "2" = "Female")

A2.1 <- lm(BodilyEmbarrassment~ Physician.Gender+Gender, data = DataA2 )
A2.2<- lm(BodilyEmbarrassment ~ Physician.Gender+Gender+Physician.Gender:Gender,data = DataA2)

anova(A2.1)

anova(A2.1,A2.2)


```

```{r,warning = FALSE, message = FALSE}
DataA2 %>% ggplot() +
aes(x = Physician.Gender, color = Gender, group = Gender, y = BodilyEmbarrassment) +
stat_summary(fun.y = mean, geom = "point") +
stat_summary(fun.y = mean, geom = "line")+
labs(y = "Embarrassment Rating", x = "Gender of Physician")+
theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle(" Patient-Gender/Physician-Gender on the examination embarassment")+
stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
scale_y_continuous(limits = c(1, 7))

```

**Adding the interaction of the Gender-PT (patient) X gender-doc  does not significanly improves the model or in other words does not explain more variance regarding how much embar or awkwardness of the private test: F(1,145)= 0.0497, p = 0.8239.**
**There is a main effect Participant's Gender on reported embarassment : F(1,146)= 4.13,p = 0.044 ;but there is no main effect of Physicain Gender on reported embarassment: F(1,146)= 0.07, p = 0.79**



3.Gender-PT X gender-doc -> were your private parts examined.
```{r,warning = FALSE, message = FALSE}
library(tidyverse)
DataA3 <- Dat_attention_check_passed %>% filter(Physician.Gender != 3 & ExaminePrivate != 3)
DataA3$ExaminePrivate = recode_factor(DataA3$ExaminePrivate, "1" = "1","2" = "0")
DataA3$Gender = recode_factor(DataA3$Gender, "1"= "Male","2" = "Female")
DataA3$Physician.Gender= recode_factor(DataA3$Physician.Gender, "1" = "Male", "2" = "Female")
A3.1<- glm(formula = ExaminePrivate~ Physician.Gender+Gender, family = "binomial",data = DataA3)
A3.2 <- glm(formula = ExaminePrivate~ Physician.Gender*Gender, family = "binomial",data = DataA3)
summary(A3.2)
#Model Comparison
anova(A3.1,A3.2,test = "Chisq")
library(ggplot2)
library(dplyr)

DataA3$ExaminePrivate = as.numeric(DataA3$ExaminePrivate)

Pivot1 = DataA3 %>%group_by(Physician.Gender,Gender) %>% summarise(ExaminePrivateRate = mean(ExaminePrivate)-1)

Pivot1%>% ggplot()+aes(x= Physician.Gender,group =Gender,color = Gender,y= ExaminePrivateRate)+
geom_point()+
geom_line()+
theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("Gender Participant/Physician on Rate of Examine Private Part")
```

**There is a significant interaction of Physician.Gender and Participant Gender in predicting whether the private part is examined. Chisq(1,385) =  7.28, p = 0.006**


4.Gender-pt X gender-doc -> chaperone present
```{r,warning = FALSE, message = FALSE}
DataA4 <- Dat_attention_check_passed %>% filter(Physician.Gender != 3 & ExaminePrivate != 3 &Chaperone.Presence != 5)
DataA4$Gender = recode_factor(DataA4$Gender, "1"= "Male","2" = "Female")
DataA4$Physician.Gender= recode_factor(DataA4$Physician.Gender, "1" = "Male", "2" = "Female")
DataA4$Chaperone.Presence = recode_factor(DataA4$Chaperone.Presence, "1" = "0", "2" = "1", "4" = "1")

A4.1<- glm(formula = Chaperone.Presence~ Physician.Gender+Gender, family = "binomial",data = DataA4)
A4.2 <- glm(formula = Chaperone.Presence~ Physician.Gender*Gender, family = "binomial",data = DataA4)

summary(A4.1)
#Model Comparison
anova(A4.1,A4.2,test = "Chisq")

DataA4$Chaperone.Presence = as.numeric(DataA4$Chaperone.Presence)

Pivot2 = DataA4 %>%group_by(Physician.Gender,Gender) %>% summarise(ChaperonePresentRate = mean(Chaperone.Presence)-1)

Pivot2%>% ggplot()+aes(x= Physician.Gender,group =Gender,color = Gender,y= ChaperonePresentRate)+
geom_point()+
geom_line()+
theme(plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
ggtitle("Gender Participant/Physician on Rate of ChaperonePresentRate")


```
**There is NO significant interaction of Physician.Gender and Participant Gender in predicting whether the Chaperone is present. Chisq(1,377) = 2.598, p = 0.11**
**There is significant Main effect of Gender in predicting whether the Chaperone is present.Specifically, if the participant gender is Female, it will increase the log odd of the rate of Chaperone present by adding 1.3**


5.Distribution of DV responses on "What is your attitude... chaperone...?"
```{r,warning = FALSE, message = FALSE}
DataA5 <- Dat_attention_check_passed %>% filter(Chaperone.Attitude!= "NA")
DataA5$Chaperone.Attitude = recode_factor(DataA5$Chaperone.Attitude, "1" = " Prefer_No", "2" = "Slightly_Prefer_No", "3" = "Prefer_ifFemale", "4" = "Prefer_ifMale", "5" = "Prefer" , "6" = "Prefer", "7" = "No Preference")

library(ggplot2)
library(dplyr)
data <- DataA5%>% 
    group_by(Chaperone.Attitude) %>% 
    summarise(count = n())

data %>% 
    ggplot(aes(x = Chaperone.Attitude, y = count)) +
    geom_col()+labs(x = "Chaperone Preference Attitue")+ggtitle("Chaperone Preference distribution" )


```

6.Gender-pt -> gender of chaperone present
```{r,warning = FALSE, message = FALSE}
DataA6 <- Dat_attention_check_passed %>% filter(Chaperone.Presence!= 1 &Chaperone.Presence!= 5)
DataA6$Chaperone.Present.Gender = recode_factor(DataA6$Chaperone.Presence, "2" = "Chaperone -Female", "4" = "Chaperone-Male")
DataA6$Gender = recode_factor(DataA6$Gender, "1" = "Participant-Male", "2" = "Participant-Female")

table(DataA6$Chaperone.Present.Gender,DataA6$Gender)

chisq.test(DataA6$Physician.Previous,DataA6$Gender)


```
**The Participant Gender did not significantly predict the Gender of chaperone present.X-squared (1)= 0.039, p-value = 0.84 **



7.Gender-pt -> chaperone was present
```{r,warning = FALSE, message = FALSE}

DataA7 <- Dat_attention_check_passed %>% filter(ExaminePrivate != 3 &Chaperone.Presence != 5)
DataA7$Gender = recode_factor(DataA7$Gender, "1"= "Male","2" = "Female")
DataA7$Chaperone.Presence = recode_factor(DataA7$Chaperone.Presence, "1" = "NO Chaperone", "2" = "Chaperone Present", "4" = "Chaperone Present")

table(DataA7$Chaperone.Presence,DataA7$Gender)
chisq.test(DataA7$Chaperone.Presence,DataA7$Gender)
```

**The Participant Gender significantly predict the Prescence of chaperone.X-squared (1)= 15.6, p-value <= 0.01**
