---
title: "Prolific Embarassment Envy Study"
author: "Juanshu Wu"
date: "5/6/2021"
output: html_document
---
#Data wrangling
```{r,warning = FALSE, message = FALSE}
#Load data
library(tidyverse)
Dat <- read.csv("Prolific-500participants-Numeric.csv",TRUE)

Dat_consent <- Dat %>% filter(Consent == 1)

mean(Dat_consent$Age) 

Dat_attention_check_passed <- Dat %>% filter(Attention1 == 1)
nrow(Dat_attention_check_passed %>% filter( Gender == 2))

library("tidyverse")
#Delete the participants' data that fail the attention checks
Dat_attention_check_passed <- Dat %>% filter(Attention1 == 1)

type_gender_know <- Dat_attention_check_passed %>% select(Gender, Prolific.ID, starts_with(c("Body","Judgment")))
#type_gender_know <- 
  #type_gender_know %>% 
 # rename(Body.Naked_1 = Body.Naked._1, Body.Naked_2 = Body.Naked._2)
test <- type_gender_know %>% select(Gender, Body.Bowel_1, Body.Bowel_2)

test %>% pivot_longer(cols=c(Body.Bowel_1, Body.Bowel_2), names_to = "doctor_type", values_to = "scores", names_prefix="Body.Bowel_")

repeated_ready1 <- 
type_gender_know %>% 
  pivot_longer(cols = starts_with(c("Judgment", "Body")), 
                 values_to = "scores", 
                 names_to = (c("Type", "Sub", "Doctor")),
               names_pattern = c("(.*)\\.(.*)_(.)"))
```


```{r,warning = FALSE, message = FALSE}
# Doctor and Type or Embarrassment on Rating

repeated_ready1$Doctor <- as.factor(repeated_ready1$Doctor)
repeated_ready1$Doctor <- recode_factor(repeated_ready1$Doctor, "1" = "NOT Know","2" = "Know")

repeated_ready1%>% 
  ggplot() +
  aes(x = Doctor, color = Type, group = Type, y = scores) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line",size = 0.8)+
  labs(y = "Embarassment Rating(1-7)")+
  theme (aspect.ratio=3/3,plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 17,face="bold"), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black",size = 1.5))+
          ggtitle("Doctor and Type of Embarassment on Rating")+
          stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
           scale_y_continuous(limits = c(1, 7))+
scale_y_continuous(limits = c(1, 7),breaks =c(1,2,3,4,5,6,7))
 
```



```{r,warning = FALSE, message = FALSE}
# Gender and Type of Embarrassment on Rating
repeated_ready1$Gender <- as.factor(repeated_ready1$Gender)
repeated_ready1$Gender<- recode_factor(repeated_ready1$Gender, "1" = "Male","2" = "Female")
repeated_ready1%>% 
  ggplot()+
  aes(x = Type, color = Gender, group = Gender, y = scores) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line",size=0.8)+
  labs(y = "Embarassment Rating(1-7)")+
  theme(aspect.ratio=3/3,plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 17,face = "bold"),panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black",size = 1.5))+ggtitle("Gender and Type of Embarassment on Rating")+stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
scale_y_continuous(limits = c(1, 7),breaks =c(1,2,3,4,5,6,7))+scale_color_manual(values=c("Blue","Red"))
   
 
```



```{r,warning = FALSE, message = FALSE}
m1 <- lmer(data=repeated_ready_avg, score_avg~1+(1|Prolific.ID))

m2 <- lmer(data=repeated_ready_avg,score_avg~Gender+(1|Prolific.ID))
anova(m1,m2)
m3 <- lmer(data=repeated_ready_avg, score_avg~Gender+Type
+(1|Prolific.ID))
anova(m1,m2)
m4<- lmer(data=repeated_ready_avg, score_avg~Gender+Type+Doctor
+(1|Prolific.ID))
anova(m1,m2)
m5<- lmer(data=repeated_ready_avg,score_avg~Gender+Type+Doctor+Gender:Type+(1|Prolific.ID))
m6<- lmer(data=repeated_ready_avg,score_avg~Gender+Type+Doctor+Gender:Type+ Type:Doctor+(1|Prolific.ID))
          
m7 <- lmer(data=repeated_ready_avg,score_avg~Gender+Type+Doctor+Gender:Type+ Type:Doctor+ Gender:Doctor+(1|Prolific.ID))
           
m8 <- lmer(data=repeated_ready_avg,score_avg~Type*Doctor*Gender+(1|Prolific.ID))

summary(m8)
anova(m8)

##Compare model:
anova(m1,m2)
anova(m2,m3)
anova(m3,m4)
anova(m4,m5)
anova(m5,m6)
anova(m6,m7)
anova(m7,m8)
install.packages("lmerTest")


fixed = y ~ A, random =  A | B/C

library(nlme)
library(tidyverse)
repeated_ready_avg <- repeated_ready1 %>% group_by(Doctor,Type,Prolific.ID,Gender)%>% summarize(score_avg = mean(scores))

lmer <- lme(score_avg~Gender+Type+Doctor+Gender:Type+ Type:Doctor+ Gender:Doctor+ Type:Doctor:Gender+(1|Prolific.ID), data = repeated_ready_avg)
anova(m1)
repeated_ready_avg$Gender = recode_factor(repeated_ready_avg$Gender, "1" = "Male", "2" = "Female")
repeated_ready_avg$Doctor = recode_factor(repeated_ready_avg$Doctor, "1" = "NotKnow ", "2" = "Know")










```        
          

```








```{r,warning = FALSE, message = FALSE}
# Doctor and SubTypes of Embarassment on Rating
repeated_ready1%>% 
  ggplot() +
  aes(x = Doctor, color = Sub, group = Sub, y = scores) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")+
  labs(y = "Embarassment Rating")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
  ggtitle("Doctor and SubTypes of Embarassment on Rating")+
  stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
   facet_wrap(.~Type)+
   scale_y_continuous(limits = c(1, 7))

 
```


```{r,warning = FALSE, message = FALSE}
model1<- aov(scores ~ Gender*Type*Doctor+Error(Prolific.ID/Type*Doctor), data = repeated_ready1)
summary(model1)
```
Significant interaction of Doctor type and Embarrassment type: F(**1**,**493**) = **145.78**, p <**0.01**
 
Significant interaction of Gender and Embarrassment type: F(**1**,**491**) = **4.87**, p = **0.0279**
 
Significant Main effect of Gender: F(**1**,**490**) = **25.11**, p < **0.01**
 
 
 
Non-Significant Main effect of Doctor type: F(**1**,**490**) = **0.16**, p  = **0.69**
 
Non- Significant Main effect of Embarrassment type: F(**1**,**491**) = **0.017**, p = **0.90**
 
Non-Significant interaction of Gender and Doctor type: F(**1**,**491**) = **1.39**, p = **0.239**

Non-Significant  three-way interaction of Gender/Doctor type/Embarrassment type: F(**1**,**491**) = **0.186**, p = **0.666**




```{r,warning = FALSE, message = FALSE}

Dat1<- Dat_attention_check_passed %>% mutate(DispEnvy = (Envy1+Envy2+Envy3+Envy4+Envy5+Envy6+Envy7+Envy8)/8)
Dat1<- Dat1 %>% mutate(EnviedPreference=(Envied.PA.Preference+Envied.FC.Preference)/2)
Dat1<- Dat1 %>% mutate(EnviedEnjoyment=(Envied.PA.Enjoyment+Envied.FC.Enjoyment)/2)


```


```{r,warning = FALSE, message = FALSE}

ggplot(Dat1, aes(x= DispEnvy, y = Dat1$Envied.Enjoyment))+
  geom_jitter()+
  labs(y = "Envied-Enjoyment-Recall", x = "mean Dispositional Envy")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
         geom_smooth(method = lm)+
         ggtitle("Recall Enjoyment of Envy / Dispositional Envy")

cor.test(Dat1$DispEnvy,Dat1$Envied.Enjoyment)


```

**Report:** Dispositional envy significantly correlated with enjoyment of being envied in the past recalled event of being envied: r(**285**) = **0.133**, p = **0.024**


```{r,warning = FALSE, message = FALSE}

ggplot(Dat1, aes(x= DispEnvy, y = Dat1$EnviedPreference))+
  geom_jitter()+
  labs(y = "Envied-Preference", x = "mean Dispositional Envy")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
         geom_smooth(method = lm)+
         ggtitle("Being Envied Preference / Dispositional Envy")

cor.test(Dat1$DispEnvy,Dat1$EnviedPreference)


```
**Report:** Dispositional envy significantly correlated with preference for being  envied-inducing situations : r(**493**) = **0.133**, p = **0.003**


```{r,warning = FALSE, message = FALSE}

ggplot(Dat1, aes(x= DispEnvy, y = Dat1$EnviedEnjoyment))+
  geom_jitter()+
  labs(y = "Envied-Enjoyment", x = "mean Dispositional Envy")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
         geom_smooth(method = lm)+
         ggtitle("Envied-Enjoyment / Dispositional Envy")


cor.test(Dat1$DispEnvy,Dat1$EnviedEnjoyment)


```
**Report:** Dispositional envy significantly correlated with preference for being  envied-inducing situations : r(**493**) = **0.23**, p < **0.001**







