---
title: "TaintedAltruismAnalysis"
author: "Juanshu Wu"
date: "5/28/2021"
output: html_document
---
## Load data and delete data who failed to consent or failed the attention check
```{r,warning = FALSE, message = FALSE}
#Load data
library(tidyverse)
Dat <- read.csv("Prolific-500participants-Numeric.csv",TRUE)
#Only keep participants who consent to participate
Dat1 <- Dat %>% filter(Consent == "1") 

#Delete the participants' data that fail the attention checks
Dat_attention_check_passed <- Dat1 %>% filter(Attention1 == 1)



```
## Create the two independent variables
```{r,warning = FALSE, message = FALSE}

# Create IV1 (Advertising/Charity)

library(dplyr)

Dat_attention_check_passed$IV1 =  recode_factor(Dat_attention_check_passed$Random1,"Charity " = "Charity ", "Advertising" = "Advertising","Advertising+Counterfactual" = "Advertising", "Charity+Counterfactual" = "Charity")

#Create IV2(Counterfactual/Non_counterfactual)

Dat_attention_check_passed$IV2 = recode_factor(Dat_attention_check_passed$Random1,
"Charity"= "Non-counterfactual", "Advertising" = "Non-counterfactual","Advertising+Counterfactual" = "Counterfactual", "Charity+Counterfactual" = "Counterfactual")

```

## Create DV-composite score(average of  questions 1-3) for each participant
```{r,warning = FALSE, message = FALSE}
#transfer the character into numeric answers
selected<-Dat_attention_check_passed%>% select(starts_with("Questions.."))
not_selected <-Dat_attention_check_passed %>% select(!starts_with("Questions.."))
selected <- 
selected %>% lapply(as.numeric)
D<- cbind(selected, not_selected)




#Split the whole sample into sample of each condition
Charity_sample <- D%>% filter(Random1 == "Charity")
Advertising_sample <- D %>% filter(Random1 =="Advertising")
Advertising_Counter <- D %>% filter(Random1 =="Advertising+Counterfactual")
CharityCounter <- D%>% filter(Random1 == "Charity+Counterfactual")


# Calculate the  for the three measurements/questions that we aggregate to form the composite score later
library(tidyverse)
D1_Charity_sample <- Charity_sample %>% select(c(Questions..1C_1,Questions..1C_2,Questions..1C_3)) 

D1 <- D1_Charity_sample %>% rename(Q1 = Questions..1C_1,Q2 = Questions..1C_2, Q3 = Questions..1C_3)
  

D2_Advertising_sample<- Advertising_sample %>% select(c(Questions..1A_1,Questions..1A_2,Questions..1A_3))

D2 <- D2_Advertising_sample %>% rename(Q1 = Questions..1A_1,Q2 = Questions..1A_2, Q3 = Questions..1A_3)


D3_Advertising_Counter <- Advertising_Counter %>% select(c(Questions..1A.C_1,Questions..1A.C_2,Questions..1A.C_3))

D3 <- D3_Advertising_Counter %>% rename(Q1 = Questions..1A.C_1, Q2 = Questions..1A.C_2, Q3 = Questions..1A.C_3)

D4_CharityCounter<- CharityCounter %>% select(c(Questions..1C.C_1,Questions..1C.C_2,Questions..1C.C_3))

D4 <- D4_CharityCounter %>% rename(Q1 = Questions..1C.C_1, Q2 = Questions..1C.C_2, Q3 = Questions..1C.C_3)

library(ltm)
#Calculate the cronbach alphas for the total sample
D_total <- rbind(D1,D2,D3,D4)
cronbach.alpha(D_total)

#Calculate the cronbach alphas for each condition sample 

cronbach.alpha(D1_Charity_sample)
cronbach.alpha(D2_Advertising_sample)
cronbach.alpha(D3_Advertising_Counter)
cronbach.alpha(D4_CharityCounter)


# calculate and mutate the composite score to each sample
Charity_sample<- Charity_sample %>% mutate(Composite_Score = (Questions..1C_1+Questions..1C_2+Questions..1C_3)/3)
Advertising_sample <- Advertising_sample %>% mutate(Composite_Score = (Questions..1A_1+Questions..1A_2+Questions..1A_3)/3) 
Advertising_Counter <- Advertising_Counter %>% mutate(Composite_Score = (Questions..1A.C_1+Questions..1A.C_2+Questions..1A.C_3)/3)
CharityCounter <- CharityCounter %>% mutate(Composite_Score = (Questions..1C.C_1+Questions..1C.C_2+Questions..1C.C_3)/3)
#combine the subsamples to get the final dataset
Data_final<- rbind(Charity_sample,
Advertising_sample,
Advertising_Counter,
CharityCounter)
 
```

## Plot to show domain(charity/advertising) and condition(counterfactual/not counterfacual) on the composite score


```{r,warning = FALSE, message = FALSE}

Data_final%>% 
  ggplot() +
  aes(x = IV1, color = IV2, group = IV2, y = Composite_Score) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")+
  labs(y = "Composite_Score")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
          ggtitle("IV1 and IV2 on DV")+
          stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
           scale_y_continuous(limits = c(1, 7))
 

Data_final%>% 
  ggplot() +
  aes(x = IV2, color = IV1, group = IV1, y = Composite_Score) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "line")+
  labs(y = "Composite_Score")+
  theme (plot.title = element_text(hjust = 0.5), text = element_text(family = "serif", size = 12), 
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(),
         panel.background = element_blank(), 
         axis.line = element_line(colour = "black"))+
          ggtitle("IV1 and IV2 on DV")+
          stat_summary(fun.data = "mean_se",geom = "errorbar", size = 0.05,width = 0.2)+
           scale_y_continuous(limits = c(1, 7))

## Mean SD for each Condition(after attention check)
Data_final%>%filter(Random1 == "Charity") %>% pull(Composite_Score)%>% mean()
Data_final%>%filter(Random1 == "Charity") %>% pull(Composite_Score)%>% sd()

Data_final%>%filter(Random1 == "Advertising")%>% pull(Composite_Score)%>% mean()
Data_final%>%filter(Random1 == "Advertising")%>% pull(Composite_Score)%>% sd()

Data_final%>%filter(Random1== "Advertising+Counterfactual")%>% pull(Composite_Score)%>% mean()
Data_final%>%filter(Random1== "Advertising+Counterfactual")%>% pull(Composite_Score)%>% sd()

Data_final%>%filter(Random1 =="Charity+Counterfactual")%>% pull(Composite_Score)%>% mean()
Data_final%>%filter(Random1 =="Charity+Counterfactual")%>% pull(Composite_Score)%>% sd()


```


#Welch Two Sample t-test 
```{r,warning = FALSE, message = FALSE}
#combine the subsamples to final datasets for t-test

Data_nocounter<- rbind(Charity_sample,
Advertising_sample
)

Data_counter<- rbind(
Advertising_Counter,
CharityCounter)


m1<-t.test(Composite_Score ~ Random1 , data=Data_nocounter, var.equal=FALSE, na.rm=TRUE)


m2<-t.test(Composite_Score ~ Random1 , data=Data_counter, var.equal=FALSE, na.rm=TRUE)


```


## Data Analysis on unbalanced design： Type III anova test

An unbalanced design has unequal numbers of subjects in each group.
There are three fundamentally different ways to run an ANOVA in an unbalanced design. They are known as Type-I, Type-II and Type-III sums of squares. All of the three should have the same result if the design is balanced, but they yield different result if the design is unbalaned.To keep things simple, note that The recommended method are the Type-III sums of squares.For Type-III, when interaction is presented, the main effect result should be interpreted with caution.

Some useful resources regarding how to deal with unbalanced design:

http://www.sthda.com/english/wiki/two-way-anova-test-in-r

http://sites.psu.edu/stat461psbsp2013/wp-content/uploads/sites/1906/2013/03/InteractionsAndTypesOfSS.pdf

https://www.r-bloggers.com/2011/03/anova-%e2%80%93-type-iiiiii-ss-explained/#:~:text=In%20general%2C%20if%20there%20is%20no%20significant%20interaction,presence%20of%20interactions%2C%20main%20effects%20are%20rarely%20interpretable%29.

```{r,warning = FALSE, message = FALSE}
library(car)
# The following two approaches of Type III yields the same result
model <- aov(Composite_Score ~ IV1*IV2, data = Data_final)
Anova(lm(Composite_Score~ IV1*IV2, data=Data_final, contrasts=list(topic=contr.sum, sys=contr.sum)),type=3)
```
**Report: There is significant interaction of IV1 and IV2 on DV: F(1,490) = 63.12, p < 0.001. **











